Advanced Calc Homework 2\\ \large 1.3.4, 1.3.7, 1.3.14, 2.1.2a, 2.1.6, 2.1.7, 2.1.15a

### 2017-02-12 311/latex/HW2.tex
Add to resume.pdf.

\title{Advanced Calc Homework 2 \large 1.3.4, 1.3.7, 1.3.14, 2.1.2a, 2.1.6, 2.1.7, 2.1.15a}
\author{Elliott Capek}
\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

@@

@@

Note that since the square of any real number is nonnegative, $\left(a-b\right) \geq 0$. Squaring both sides yields $a^2 + b^2 - 2ab \geq 0$, and so $ab \leq \frac12\left(a^2+b^2\right$, as desired.\\

@@

@@

>>>>

\title{Advanced Calc Homework 2\\ \large 1.3.4, 1.3.7, 1.3.14, 2.1.2a, 2.1.6, 2.1.7, 2.1.15a}
\author{Elliott Capek}
\titlespacing{\section}{0pt}{0pt}{5pt} % Spacing around titles

@@

\section{Problem 1.3.2}
For $a > 0$, we want to show that $|x - a| < \frac a2$ then $x > \frac a2$.\\

Let $|x - a| < \frac a2$. Then by Proposition 1.2 this is equivalent to statement $a - \frac a2 < x < a + \frac{3a}{2}$, thus $x > \frac a2$, as desired.\\

\section{Problem 1.3.7}
Starting with statement $(a+b) + (-b)$, apply the triangle inequality to get $|a+b| + |-b| \geq |a + b -b| = |a|$. By rearranging terms, we get $|a| - |b| \leq |a+b|$.\\

Now interchanging $a$ and $b$ yields $|b| - |a| \leq |b+a|$. By algebra, $-\left(|a| - |b|\right) \leq |a+b|$. Then $\left||a| - |b|\right| \leq |a+b|$.\\

@@

Note that since the square of any real number is nonnegative, $\left(a-b\right) \geq 0$. Squaring both sides yields $a^2 + b^2 - 2ab \geq 0$, and so $ab \leq \frac12\left(a^2+b^2\right)$, as desired.\\

@@

\newpage

@@

\section{Problem 2.1.15a}
We want to show the polynomial $a_n = n^3 - 4n^2 - 100n$ converge to infinity, or that $\forall c \in \mathbb{R}, c> 0$, $\exists N$ such that $\forall n \geq N$, $a_n > c$.\\

Consider $a_n$ and its derivatives:\\

\begin{align*}
  a_n &= n^3 - 4n^2 - 100n\\
  a_n' &= 3n^2 - 8n - 100\\
  a_n'' &= 6n - 8\\
  a_n''' &= 6\\
  a_n'''' &= 0
\end{align*}

Notice that, at $n=100$, it is the case that $a_n >0$, $a_n' > 0$, $a_n'' > 0$, $a_n''' > 0$ and $a_n'''' = 0$. Because the third derivative is a constant positive number, $a_n$ where $n > 100$ will always increase at an increasing rate. Thus for any $c < 100$, $N = 100$ satisfies the claim.\\

Now consider for any $c > 100$, because $a_n$ is increasing at a steadily increasing rate, there must exist some $n'$ such that $a_{n'} = c$. Now for all $n > n'$, $a_n > c$, so the claim is also satisfied for $c > 100$. Thus $a_n$ converges at infinity.\\
